---
title: "Data Scientists vs Statisticians"
format: html
editor: visual
---

## Data Science Questions

Below are my answers to the data science vs statistics questions.

<ol>

<li>
I typically think of a data scientist as an individual that handles the programming required to manage a large amount of data. I imagine them as some type of contracter or consultant for another company.
</li>

<li>
There is a large overlap between the fields of data science and statistics. Both groups use the same programming languages and analyze data. However, in data science there is a greater emphasis on programming, while in statistics there is greater emphasis on the underlying mathematical principles.
</li>

<li>
As a statistics student, I identify more as a statistician, given the courses I have taken in statistical theory. However, the technology associated with the field of data science allows for so much analysis to be done on such a large scale that most statisticians probably consider themselves somewhat of a data scientist, and vice versa.
</li>

</ol>

## Iris Data Set

As instructed, we create the object y from the Iris data set.

We determine the class, type, and structure of y.

```{r}
y <- density(iris$Petal.Width)
class(y)
typeof(y)
str(y)
```

We plot the y and use echo:false to keep the R code from being displayed in the document rendered.

```{r}
#| echo: false
plot(y)
```

The `echo: false` option disables the printing of code (only output is displayed).
